Composition-climate paper

### 2015-07-07 Composition_Ecology.Rmd
Minor changes to the figure functions so that the figures are generated from the code itself, not linked in.
Re-numbered figures in text.

---
title: "Composition-climate paper"
author: "Simon Goring *et al*."
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  md_document:
    variant: markdown
  pdf_document:
    pandoc_args: "-V geometry:vmargin=1in -V geometry:hmargin=1in"
pandoc_args: "-H margins.sty"
bibliography: goringetal_references.bib
csl: ecology.csl
---

@@

```{r, echo = FALSE, warning = FALSE, message = FALSE, message=FALSE}
# Load climate data and generate the pre-sett and modern bounds:
#  Pre-settlement climate: 1900 - 1930
#  Modern climate: 1960 - 1990

@@

```{r}

@@

```
**Figure 1.** *Patterns of land use change in the upper Midwestern United States. Data from the NLCD [@jin2013comprehensive].*

@@

```
![](figures/clim_plot.tiff)
**Figure 1**. *Climate change in the Upper Midwest over the last two centuries using PRISM data and North American Drought Atlas PDSI reconstructions.  Low temperatures in the 1970s result in lower T_max_ during the modern era, but climate change has resulted in higher T_min_ values than the early-century normals, along with increasing A_ppt_.  PDSI shows strong coherence with A_ppt_ in this region.*

@@

loss_table <- as.data.frame.matrix(table(loss_melt$variable, loss_melt$value))
loss_table$Gain <- loss_table$Gain / (loss_table$Loss + loss_table$Presence)
loss_table[,2:3] <- tran(loss_table[,2:3], method = 'proportion')

```
![](figures/loss_plots.tiff)

**Figure 2**.  *Gain loss and continuous presence for PLSS and FIA tree taxa. Continuous presence is indicated by dark green.  For most taxa it is the central parts of their distribution that show continuous presence.  Few taxa show novel presence (purple), although taxa such as poplar, ash and basswood do show gains of over 10%.  Most taxa show significant losses in distribution (orange).*

@@

**Figure 3** *Changes in the overall climate space in the upper midwestern United States. The climate densities largely overlap, although it is possible to see the shifts in precipitation, mean and minium temperatures, where FIA data (pink) has higher values), while the decline in maximum temperatures is also visible, largely at the very highest values.*

@@

**Figure X**. *For each of the four variables examined we see...*

>>>>

---
title: "Composition-climate paper"
author: "Simon Goring *et al*."
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  word_document:
    fig_width: 6
    fig_height: 6
  md_document:
    variant: markdown_github
  pdf_document:
    pandoc_args: "-V geometry:vmargin=1in -V geometry:hmargin=1in"
pandoc_args: "-H margins.sty"
bibliography: goringetal_references.bib
csl: ecology.csl
---

@@

```{r, echo = FALSE, warning = FALSE, message=FALSE, results='hide'}
# Load climate data and generate the pre-sett and modern bounds:
#  Pre-settlement climate: 1900 - 1930
#  Modern climate: 1960 - 1990

@@

```{r figure1, fig.width=6, fig.height=5, echo = FALSE, warning = FALSE, message=FALSE}

@@

**Figure 1.** *Patterns of land use change in the upper Midwestern United States. Data from the NLCD [@jin2013comprehensive].*

@@

climate_values$plot

**Figure 2.**. *Climate change in the Upper Midwest over the last two centuries using PRISM data and North American Drought Atlas PDSI reconstructions.  Low temperatures in the 1970s result in lower T_max_ during the modern era, but climate change has resulted in higher T_min_ values than the early-century normals, along with increasing A_ppt_.  PDSI shows strong coherence with A_ppt_ in this region.*

@@

loss_table <- as.data.frame.matrix(table(loss_melt[[1]]$variable, loss_melt[[1]]$value))
loss_table$Gain <- loss_table$Gain / (loss_table$Loss + loss_table$Presence)
loss_table[,2:3] <- tran(loss_table[,2:3], method = 'proportion')

loss_melt[[2]]
```

**Figure 3.**.  *Gain loss and continuous presence for PLSS and FIA tree taxa. Continuous presence is indicated by dark green.  For most taxa it is the central parts of their distribution that show continuous presence.  Few taxa show novel presence (purple), although taxa such as poplar, ash and basswood do show gains of over 10%.  Most taxa show significant losses in distribution (orange).*

@@

**Figure 4.** *Changes in the overall climate space in the upper midwestern United States. The climate densities largely overlap, although it is possible to see the shifts in precipitation, mean and minium temperatures, where FIA data (pink) has higher values), while the decline in maximum temperatures is also visible, largely at the very highest values.*

@@

**Figure 5**. *For each of the four variables examined we see...*
